Liveness-Based Garbage Collection for Lazy Languages

### 2015-11-29 paper/paper.tex
added missing file

A variable is {\em live} if there  is a possibility of its value being
used in  future computations and  dead if  it is definitely  not used.
Heap-allocated data  needs a richer model  than classical liveness---a
model  which  talks  about  liveness of  references.   Using  $\acar$,
$\acdr$  to  represent access  using  $\CAR$  and $\CDR$  fields,  the
liveness of the structure reachable from a variable can be represented
by a set of {\em access paths} i.e.  prefix-closed set of strings from
$\{\acar,\acdr\}^\ast$.  Given an initial location $\ell$ (typically a
variable  reference) and  a heap  \heap, semantically  an access  path
$\alpha$ represents  a reference, denoted $\heap\llbracket\ell,  \alpha\rrbracket$, in
the heap  that is  obtained by  starting with  $\ell$ and  chasing the
\CAR\ or  \CDR\ fields in the heap as specified  by the  access path.  
$\heap\llbracket\ell, \alpha\rrbracket$  is defined only  if the path followed  in the
heap  is \emph{closure-free}  (does not  cross closures),  else it  is
undefined.

@@

As noted earlier, $x.\alpha \in  \Lv_y$ specifies the liveness  of the
reference $\heap\llbracket\rho(x), \alpha\rrbracket$  only if $\alpha$ corresponds to  a closure-free path
in \heap\   starting from $\rho(x)$.  If this  path is intercepted  by a
closure,  say  $\CAR~{x_{\pi}}$, then  the  liveness  of further  heap
contents starting from $\mathit{x_{\pi}}$ is given by $\Lv_\mathit{x_{\pi}}$.

@@

It is clear that if the TM given as an instance of the halting problem
accepts the input string, then the earlier derivation can be replayed,
every time replacing   $\nont{\mathit{\mathit{all}}}{}$   in   the  sentential   form   by
$\epsilon$. Conversely,  if the TM  does not accept the  input string,
then  any sentential  form derived  from the  start symbol  would have
exactly one non-terminal, and this non-terminal will be different from
$\nont{\mathit{final}}{c}$.  Thus  the  empty   string  would  not  be
derivable from the grammar.
\end{proof}

>>>>

A variable is {\em live} if there  is a possibility of its value being
used in  future computations and  dead if  it is definitely  not used.
Heap-allocated data  needs a richer model  than classical liveness---a
model  which  talks  about  liveness of  references.   Using  $\acar$,
$\acdr$  to  represent access  using  $\CAR$  and $\CDR$  fields,  the
liveness of the structure reachable from a variable can be represented
by a set of {\em access paths} i.e.  prefix-closed set of strings from
$\{\acar,\acdr\}^\ast$.  Given an initial location $\ell$ (usually a 
reference corresponding to a variable) and  a heap  \heap, semantically  an access  path
$\alpha$ represents  a reference, denoted $\heap\llbracket\ell,  \alpha\rrbracket$, in
the heap  that is  obtained by  starting with  $\ell$ and  chasing the
\CAR\ or  \CDR\ fields in the heap as specified  by the  access path.  
$\heap\llbracket\ell, \alpha\rrbracket$  is defined only  if the path followed  in the
heap  is \emph{closure-free}  (does not  cross closures),  else it  is
undefined.

@@

As noted earlier, $x.\alpha \in  \Lv_y$ specifies the liveness  of the
reference $\heap\llbracket\rho(x), \alpha\rrbracket$  only if $\alpha$ corresponds to  a closure-free path
in \heap\   starting from $\rho(x)$.  If this  path is intercepted  by a
closure,  say  $(\CAR~{x_{\pi}})$, then  the  liveness  of further  heap
contents starting from $\mathit{x_{\pi}}$ is given by $\Lv_\mathit{x_{\pi}}$.

@@

It is clear that if the TM given as an instance of the halting problem
accepts the input string, then the earlier derivation can be replayed,
every time replacing   $\nont{\mathit{\mathit{all}}}{}$   in   the  sentential   form   by
$\epsilon$. However,  if the TM  does not accept the  input string,
then  any sentential  form derived  from the  start symbol  would have
exactly one non-terminal, and this non-terminal will be different from
$\nont{\mathit{final}}{c}$.  Thus  the  empty   string  would  not  be
derivable from the grammar.
\end{proof}
